---
title: "Vis I"
output: github_document
date: "2024-10-10"
---

```{r setup, include=FALSE}
library(tidyverse)
```



Import the weather data 
```{r}
remotes::install_github("ropensci/rnoaa", force = TRUE)

weather_df = read_csv(file = "weather_df.csv")

write_csv(weather_df, file = "weather_df.csv")
```

Making our first plot 
```{r}
ggplot(weather_df, aes(x = tmin, y = tmax)) + 
  geom_point()
```

This does the same thing - 
```{r}
ggp_weather = 
  weather_df |>
  ggplot(aes(x = tmin, y = tmax)) + 
  geom_point()
``` 

#Advanced Scatterplot 
```{r}
weather_df |>
  ggplot(aes(x = tmin, y = tmax, color = name)) + 
  geom_point(alpha = 0.3, size = 0.8) + 
  geom_smooth(se = FALSE)
```
geom_smooth gives you a smooth curve

Where you define aes matters
```{r}
weather_df |>
  ggplot(aes(x = tmin, y = tmax)) + 
  geom_point(aes(color = name), alpha = .5) +
  geom_smooth(se = FALSE)
```

use faceting real quick 
```{r}
weather_df |>
  ggplot(aes(x = tmin, y = tmax, color = name)) + 
  geom_point(alpha = 0.3, size = 0.8) + 
  geom_smooth(se = FALSE) + 
  facet_grid(. ~ name)
```
. means everything, then ~ siginifies columns. So basically we are separating panels for each park name 

Lets make a more interesting scatterplot 
```{r}
weather_df |> 
  ggplot(aes(x = date, y = tmax, color = name, size = prcp)) + 
  geom_point(alpha = 0.3) +
  geom_smooth(se = FALSE) + 
  facet_grid(. ~ name)
```

#Learning Assesment: Data processing and making a plot\
```{r}
weather_df |> 
  filter(name == "CentralPark_NY") |> 
  mutate(
    tmax_fahr = tmax * (9 / 5) + 32,
    tmin_fahr = tmin * (9 / 5) + 32) |> 
  ggplot(aes(x = tmin_fahr, y = tmax_fahr)) +
  geom_point(alpha = .5) + 
  geom_smooth(method = "lm", se = FALSE)
```